% ========================================================================================
%   Resume in Latex
%   Author : Jake Gutierrez
%   Based off of: https://github.com/sb2nov/resume
%   License : MIT
% ========================================================================================

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


% ------------------------------------- FONT OPTIONS -------------------------------------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% -------------------------------------- PAGE SETUP --------------------------------------
\pagestyle{fancy}
\fancyhf{}  % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


% ------------------------------------ CUSTOM COMMANDS -----------------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingRow}[7]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
      \textit{\small#7} & \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\reusmeSubHeadingListSmallStart}{\begin{itemize}[itemsep=-4pt, parsep=4pt]}
\newcommand{\resumeSubHeadingListSmallEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


% ========================================================================================
%                                   RESUME STARTS HERE
% ----------------------------------------------------------------------------------------

\begin{document}

% --------------------------------------- HEADING ----------------------------------------

\begin{center}
    {\LARGE \scshape Tony Kabilan Okeke} \\  
    \vspace{1pt}
    Philadelphia, PA \\ 
    \vspace{1pt}
    \href{mailto:tko35@drexel.edu}{\faEnvelope\  tko35@drexel.edu}
    ~~
    \href{https://linkedin.com/in//t-k-o}{\faLinkedin\ linkedin.com/in/t-k-o}
    ~~
    \href{https://github.com/Kabilan108}{\faGithub\ Kabilan108}
    \vspace{-18pt}
\end{center}


% -------------------------------------- EDUCATION ---------------------------------------

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheadingRow
        {Drexel University}
        {Philadelphia, Pennsylvania}
        {Master/Bachelor of Science in Biomedical Engineering}
        {Anticipated Graduation: June 2024}
        {Concentrations: Bioinformatics \& Neuroengineering} 
        {Cummulative GPA: 4.00}
        {Minor: Computer Science}
\resumeSubHeadingListEnd


% -------------------------------------- EXPERIENCE --------------------------------------

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {IVIVT - Non-Clinical Safety - Global Investigative Safety, GSK} 
    {April 2022 -- September 2022}
    {Scientific Student Worker} 
    {Collegeville, Pennsylvania}

    \resumeItemListStart
        \resumeItem{
            Utilized the \textit{Dash} and \textit{Flask} libraries in python to develop 
            an interactive web application for performing statistical analysis on data 
            generated in high-content imaging toxicology studies. Also utilized 
            \textit{Dask} to parallelize computations on larger data sets to improve 
            efficiency. The web application was then deployed via \textit{RStudio Connect} 
            on the internal HPC.
        }
        \resumeItem{
            Trained the \textit{Noise2Void} deep neural network on HPC to perform noise 
            reduction in microscopy images in order to improve the accuracy of CellProfiler
            pipelines for image segmentation and feature extraction.
        }
        \resumeItem{
            Developed a python package with tools for performing statistical analysis, 
            visualization, and machine learning on high-content imaging data sets.
        }
        \resumeItem{
            Implemented pipelines in \textit{CellProfiler} and \textit{Columbus} to 
            perform feature extraction for high-content images generated via cell painting 
            assays.
        }
        \resumeItem{
            Utilized \textit{Scikit-learn} to implement decision tree, random forest, and 
            support vector machine models for biomarker discovery on high-content imaging 
            datasets.
        }
    \resumeItemListEnd
  
\resumeSubheading
    {Invenio Lab, Hospital of the University of Pennsylvania}
    {March 2021 -- August 2022}
    {Immunology Research Assistant}
    {Philadelphia, Pennsylvania}

    \resumeItemListStart
        \resumeItem{
            Utilized \emph{Scikit-learn}, \emph{Pandas} and \emph{NumPy} to apply 
            unsupervised learning algorithms to clinical and multi-omic datasets, and 
            presented results to colleagues using \emph{Seaborn} in \emph{Jupyter} 
            notebooks.
        }
        \resumeItem{
            Developed \emph{R} scripts for analyzing protein expression and clinical data 
            from electronic medical records.
        }
        \resumeItem{
            Performed differential methylation, KEGG pathway enrichment, and Gene Ontology 
            analysis on microarray results for patients who underwent cardiopulmonary 
            bypass surgeries using \emph{bash} and \emph{R} scripts.
        }
    \resumeItemListEnd
  
\resumeSubheading
    {Zhou Lab, Children's Hospital of Philadelphia}
    {May 2020 -- June 2021}
    {Undergraduate Research Intern}
    {Philadelphia, Pennsylvania}

    \resumeItemListStart
        \resumeItem{
            Contributed to the development of R packages for analyzing DNA methylation 
            levels in data from Illumina microarrays.
        }
        \resumeItem{
            Validated R package performance using \emph{GEO} public datasets.
        }
    \resumeItemListEnd
    
\resumeSubHeadingListEnd
\vspace{-10pt}


% --------------------------------------- PROJECTS ---------------------------------------

\section{Projects}
\vspace{-5pt}

\resumeSubHeadingListStart
        
\resumeProjectHeading
    {\textbf{ELISA Analysis Tool} $|$ \emph{R, Shiny}} {September 2021}
    \resumeItemListStart
        \resumeItem{
            Processed Optical Density values from microplate readers using \emph{tidyverse}
            packages.
        }
        \resumeItem{
            Developed \emph{R} script for fitting OD values for ELISA standards to a 
            5-Parameter logistic regression model to estimate unknown sample 
            concentrations.
        }
        \resumeItem{
            Built interactive web-application for ELISA curve fitting using the 
            \emph{RShiny} framework.
        }
    \resumeItemListEnd
    \vspace{-16pt}

\resumeSubHeadingListEnd
\vspace{2pt}


% ---------------------------------------- SKILLS ----------------------------------------

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Programming Languages: }{
            Python, R, Bash, C++, MATLAB, SQL, AWK, Git, PHP
        } \\
        \textbf{Software: }{
            CellProfiler, Columbus Imaging Software, Microsoft Office, LoggerPro, 
            Simulink, Fusion 360, Ultimaker Cura
        } \\
    }}
 \end{itemize}
 \vspace{-15pt}


% ------------------------------------- PUBLICATIONS--------------------------------------

\section{Publications}
\vspace{-3pt}

\reusmeSubHeadingListSmallStart
    \item\small {
        \emph{
            Longitudinal urinary biomarkers of immunological activation in COVID-19
            patients without clinically apparent kidney disease versus acute and 
            chronic failure.
        } 
        \href{https://www.nature.com/articles/s41598-021-99102-5.pdf?proof=tr} 
        {Scientific Reports 11, 19675 (2021)}.
    }
    
    \item\small {
        \emph{
            Unbiased Analysis of Temporal Changes in Immune Serum Markers in Acute 
            COVID-19 Infection With Emphasis on Organ Failure, Anti-Viral Treatment, 
            and Demographic Characteristics.
        } 
        \href{https://www.frontiersin.org/articles/10.3389/fimmu.2021.650465/full} 
        {Frontiers in Immunology 12:650465 (2021)}.
    }
\resumeSubHeadingListSmallEnd

\vspace{-20pt}


% ------------------------------------- PUBLICATIONS--------------------------------------

\section{Activities}

\reusmeSubHeadingListSmallStart
\vspace{-3pt}    
    \item\small {
        Vice President, \emph{Drexel Computational Design}, March 2021 -- Present
    }
    \item\small {
        Member, \emph{Tau Beta Pi}, December 2021 -- Present
    }
    \item\small {
        Member, \emph{Drexel Society of Artificial Intelligence}, September 2022 -- Present
    }
\resumeSubHeadingListSmallEnd


\end{document}

% ----------------------------------------------------------------------------------------
%                                    RESUME ENDS HERE
% ========================================================================================
