%-------------------------
% Resume in Latex
% Author : Tony Kabilan Okeke
%
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}   
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{fontawesome5}
\usepackage[utf8]{inputenc}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage[
    hidelinks,
    pdfinfo={
        Title={Tony K Okeke - Resume},
        Author={Tony Kabilan Okeke},
        Keywords={resume, Tony Okeke, data science, machine learning, deep learning, NLP, bioinformatics, computational biology, spatial transcriptomic, single-cell RNA-seq}
    }]{hyperref}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingRow}[7]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \renewcommand{\arraystretch}{0.2}% Reduce the spacing between rows
      \textbf{#1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
      {\small#5} & {\small #6} \\
      {\small#7} & \\
    \end{tabular*}\vspace{-7pt}
}
% \newcommand{\resumeSubheadingRow}[7]{
%   \vspace{-2pt}\item
%     \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & \textbf{\small #2} \\
%       {\small#3} & {\small #4} \\
%       {\small#5} & {\small #6} \\
%       {\small#7} & \\
%     \end{tabular*}\vspace{-7pt}
% }

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \href{https://kabilan108.com}{\LARGE \scshape Tony Kabilan Okeke} \\  
    \vspace{1pt}
    Philadelphia, PA \\ 
    \vspace{1pt}
    \href{mailto:tonykabilanokeke@gmail\.com}{\faEnvelope\  tonykabilanokeke@gmail\.com}
    ~~
    \href{https://linkedin.com/in//t-k-o}{\faLinkedin\ linkedin.com/in/t-k-o}
    ~~
    \href{https://github.com/Kabilan108}{\faGithub\ Kabilan108}
    \vspace{-18pt}
\end{center}


  

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Bioinformatics Data Scientist} {}
        {GSK \textbar{} Collegeville, PA} {Apr 2022 -- Sep 2022 \textbar{} Apr 2023 -- Sep 2023}
    \resumeItemListStart
        \resumeItem {
            Developed data integration pipelines to enable joint analysis of internally generated spatial transcriptomics (10X Visium, GeoMx) data with public scRNA-seq datasets, providing novel biological insights.
        }
        \resumeItem {
            Developed machine learning models to predict carcinogenicity-initiating events for target molecules using rat transcriptomics data and chemical structures. Identified compound subgroups using UMAP embeddings.
        }
        \resumeItem {
            Built a web-based tool for performing statistical analysis and biomarker discovery on high-content imaging datasets using \emph{Dash} and \emph{Flask},  with \emph{Dask} to scale computations. Deployed on \emph{R Studio Connect}.
        }
        \resumeItem {
            Trained and deployed machine learning models (Decision Trees, Random Forests, SVMs) to identify imaging biomarkers in safety toxicology studies.
        }
        \resumeItem {
            Implemented deep learning models (Noise2Void, Cellpose) to improve the performance of \emph{CellProfiler} segmentation and feature extraction pipelines.
        }
    \resumeItemListEnd
  
    \resumeSubheading
        {Computational Research Assistant}{}
        {Penn Medicine \textbar{} Philadelphia, PA}{Mar 2021 -- Aug 2022}
    \resumeItemListStart
        % \resumeItem {
        %     Spearheaded data analysis efforts resulting in four \href{https://scholar.google.com/citations?user=kPKT6SsAAAAJ}{peer-reviewed publications}, providing novel insights into COVID-19 immune response, including serum and urinary biomarkers, and neurological impacts.
        % }
        \resumeItem {
            Developed Python and R scripts to automate data ingestion, quality control and analysis for ELISA and Next-Generation Sequencing (NGS) assays, resulting in a 4X speed up of existing workflows. Conducted differential methylation and pathway enrichment analyses on NGS datasets.
        }
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-13pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{AbokiCode} \textbar{} Transformers, FastAPI, Telegram Bot API \textbar{} Hackathon Winner} {Sep 2023 -- Present}
    \resumeItemListStart
        \resumeItem {
            Developed a Learning Management System to facilitate easy course delivery to students in low-income areas. Implemented a web app using Next.js to enable course instructors customize the interface for students.
        }
        \resumeItem {
            Built LLM-based study assistant to aid students with questions related to course material. Utilized LlamaIndex to build retrieval augmented generation pipeline using ColBERT embeddings stored in MongoDB. Served assistant via FastAPI.
        }
    \resumeItemListEnd
    \vspace{-15pt}

    \resumeProjectHeading
        {\textbf{Meddibia} \textbar{} Tensorflow, Flask, Flutter \textbar{} Hackathon Winner} {Mar 2023}
    \resumeItemListStart
        \resumeItem {
            Developed a medical diagnostic tool with a Flask API serving a Flutter-based IOS app.
        }
        \resumeItem {
            Fine-tuned neural networks (VGG16, EfficientNet) for skin lesion detection, achieving 70\% accuracy. Developed API endpoints that leverage GPT-3 to extract symptoms from user messages. Trained a Naive Bayes classifier to predict diseases given a list of symptoms with 80\% accuracy.
        }
    \resumeItemListEnd
    \vspace{-15pt}

    \resumeProjectHeading
        {\textbf{ML for Predicting Gene Ontology Enrichment} \textbar{} Tensorflow, Flask, Flutter} {Sep 2022}
    \resumeItemListStart
        \resumeItem {
            Developed an end-to-end pipeline for processing and analyzing over 11,000 RNA-seq datasets, leveraging high-memory GCP VMs to process datasets in batches.
        }
        \resumeItem{
            Trained and optimized an autoencoder neural network to reconstruct log fold-change values and predict Gene Ontology (GO) enrichment using latent space features.
        }
    \resumeItemListEnd
    \vspace{-15pt}

    \resumeProjectHeading
        {\textbf{Identification of Connectomic Biomarkers for Autism using ML} \textbar{} bctpy, scikit-learn} {Aug 2022}
    \resumeItemListStart
        \resumeItem {
            Computed graph theory measures on structural connectomes from ASD patients and employed machine learning models (LASSO, SVM) for feature selection and diagnostic accuracy assessment.
        }
        \resumeItem {
            Conducted a comprehensive study correlating connectomic biomarkers with clinical outcomes, utilizing data visualization tools to represent intricate relationships within the multimodal dataset.
        }
    \resumeItemListEnd
    \vspace{-7pt}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheadingRow
        {Drexel University} {Philadelphia, Pennsylvania}
        {Master of Science in Biomedical Engineering} {Graduation: June 2024}
        {Bachelor of Science in Biomedical Engineering} {GPA: 4.00}
        {Concentrations: Biomedical informatics \& Neuroengineering}
\resumeSubHeadingListEnd
\vspace{-9pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{multicols}{2}
    \begin{itemize}[leftmargin=0.1in, itemsep=-3pt, label={}]
        \item\small {
            \textbf{Programming:} {Python, R, C++, SQL, Js/Ts, Shell, MATLAB} \\
        }
        \item\small {
            \textbf{Bioinformatics:} {Seurat, ScanPy, SquidPy, CellProfiler}
        }
    \end{itemize}
    
    \columnbreak
    
    \begin{itemize}[leftmargin=0.1in, itemsep=-3pt, label={}]
        \item\small {
            \textbf{Web:} {Flask, FastAPI, React.js, Next.js}
        }
        \item\small {
            \textbf{AI/ML:} {PyTorch, TensorFlow, sklearn, WandB, LangChain}
        }
    \end{itemize}
\end{multicols}
 \vspace{-6pt}
   
%-----------INVOLVEMENT---------------
\section{Clubs \& Organizations}
\begin{itemize}[leftmargin=0.2in, itemsep=-4pt]
    \item\small Vice President, \emph{Drexel Computational Design}, March 2021 -- Present
    \item\small Member, \emph{Sigma Xi}, January 2024 -- Present
    \item\small Member, \emph{Tau Beta Pi}, December 2021 -- Present
\end{itemize}
 
\end{document}
